---
title: "Distribution of v1-v4 difference"
author: "Xinyi Lin"
date: "2/6/2020"
output: html_document
---

```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(ggplot2)
library(patchwork)
```

```{r}
pairAlign_res <- read.csv("D:/Codes/korem_16s/Data/pairwise_alig_res.csv")
head(pairAlign_res,15)
```

## Find the copies combination with largest difference

record_id: NCBI assembly accession
copies: combination of 16s copies used for pairwise sequence alignment
distance: distance between start points of copies
v1v2_diff: numbers of different sites between two copies in v1/v2 region
v3v4_diff: numbers of different sites between two copies in v3/v4 region
max: this combination shows largest different sites number in which region

```{r}
max_v1v2 = pairAlign_res %>% 
  group_by(record_id) %>% 
  filter(v1v2_diff == max(v1v2_diff)) %>% 
  mutate(max = "v1v2") %>% 
  ungroup()
max_v3v4 = pairAlign_res %>% 
  group_by(record_id) %>% 
  filter(v3v4_diff == max(v3v4_diff)) %>% 
  mutate(max = "v3v4") %>% 
  ungroup()
max_pairAlign_res = rbind(max_v1v2,max_v3v4) %>% 
  arrange(record_id)
max_pairAlign_res %>% 
  head(15)
```

```{r}
write.table(max_pairAlign_res, file = "D:/Codes/korem_16s/Data/max_pairAlign_res.txt", append = FALSE, quote = FALSE, row.names = FALSE)
```

## Draw distribution of difference

### v1v2 region

For distance larger than 150kbp:

```{r,message=FALSE}
pairAlign_res$v1v2_diff %>% summary()
pairAlign_res$v3v4_diff %>% summary()
pairAlign_res %>% 
  group_by(v1v2_diff) %>% 
  summarize(n = n())
small_10 = pairAlign_res %>% 
  filter(v1v2_diff<=10) %>% 
  ggplot(aes(v1v2_diff)) +
  geom_histogram() + 
  scale_x_continuous(breaks=seq(0, 10, 1)) +
  xlab("v1v2 difference(0-10)")
larg_10 = pairAlign_res %>% 
  filter(v1v2_diff>10) %>% 
  ggplot(aes(v1v2_diff)) +
  geom_histogram() +
  xlab("v1v2 difference(10+)")
small_10 + larg_10
```

For distance larger than 200kbp:

```{r,message=FALSE}
pairAlign_res %>% 
  filter(distance > 200000) %>% 
  group_by(v1v2_diff) %>% 
  summarize(n = n())
small_10 = pairAlign_res %>% 
  filter(distance > 200000) %>% 
  filter(v1v2_diff<=10) %>% 
  ggplot(aes(v1v2_diff)) +
  geom_histogram() + 
  scale_x_continuous(breaks=seq(0, 10, 1)) +
  xlab("v1v2 difference(0-10)")
larg_10 = pairAlign_res %>% 
  filter(distance > 200000) %>% 
  filter(v1v2_diff>10) %>% 
  ggplot(aes(v1v2_diff)) +
  geom_histogram() +
  xlab("v1v2 difference(10+)")
small_10 + larg_10
```

### v3v4 region

For distance larger than 150kbp:

```{r,message=FALSE}
pairAlign_res %>% 
  group_by(v3v4_diff) %>% 
  summarize(n = n())
small_10 = pairAlign_res %>% 
  filter(v3v4_diff<=10) %>% 
  ggplot(aes(v3v4_diff)) +
  geom_histogram() + 
  scale_x_continuous(breaks=seq(0, 10, 1)) +
  xlab("v3v4 difference(0-10)")
larg_10 = pairAlign_res %>% 
  filter(v3v4_diff>10) %>% 
  ggplot(aes(v3v4_diff)) +
  geom_histogram() +
  xlab("v3v4 difference(10+)")
small_10 + larg_10
```

For distance larger than 200kbp:

```{r,message=FALSE}
pairAlign_res %>% 
  filter(distance > 200000) %>% 
  group_by(v3v4_diff) %>% 
  summarize(n = n())
small_10 = pairAlign_res %>% 
  filter(distance > 200000) %>% 
  filter(v3v4_diff<=10) %>% 
  ggplot(aes(v3v4_diff)) +
  geom_histogram() + 
  scale_x_continuous(breaks=seq(0, 10, 1)) +
  xlab("v3v4 difference(0-10)")
larg_10 = pairAlign_res %>% 
  filter(distance > 200000) %>% 
  filter(v3v4_diff>10) %>% 
  ggplot(aes(v3v4_diff)) +
  geom_histogram() +
  xlab("v3v4 difference(10+)")
small_10 + larg_10
```